---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fortunator

<!-- badges: start -->
<!-- badges: end -->

Have you already memorised all qutoes int the [fortunes](https://cran.r-project.org/web/packages/fortunes/index.html) package and you are hungry for more? fortunator is for you! Using our higly advanced AI™ and Machine Learning™ algorithm, we've developed a function that can create literally["literal] infinite fortunes!

[^literal]: figuratively

## Installation

You can install the latest, shiniest version of fortunator from [GitHub](https://github.com/) with:

``` r
devtools::install_github("eliocamp/fortunator")
```

## Example

Using fortunator couldn't be easier just load the library and start enjoying deep, thoughful quotes about your faviourite programming language!

```{r example}
library(fortunator)

fortunator(seed = 943)
fortunator(611)
fortunator(339)
```

If you want unreproducible wisdom, then you can omit the seed and be surprised every time!

```{r include=FALSE}
set.seed(123)
```

```{r}
fortunator()
```

